Supplementary materials for the paper ``Uncertainty propagation in neural networks for sparse coding''

### 2018-05-14 paper/supplementary.tex

\begin{figure}[h]
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
\caption{Approximations of the Bayesian \textsc{lista}}
%\label{fig:z_new_testing}
\end{figure}

@@

\section{Posterior estimation for the \textsc{mnist} data}
Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.

@@

>>>>

\begin{figure}[h]
\centering
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.4\columnwidth]{d_testing}\label{fig:d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.4\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
\caption{Approximations of the Bayesian \textsc{lista}}
%\label{fig:z_new_testing}
\end{figure}

@@

\section{Additional results on the \textsc{mnist} data}
In contrast to \textsc{lista} and baselines, the Bayesian \textsc{lista} provides a posterior estimate for a test data point. Figure~\ref{fig:posterior_samples} shows samples from the posterior for the test image of the digit $7$ and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.

@@

Here we also provide the comparison of the Bayesian and non-Bayesian \textsc{lista} networks in terms of the clock time for the experiment with $K = 250$ on the \textsc{mnist} data (Figure~\ref{fig:mnist_time}).

\begin{figure}[h]
\centering
\subfloat[]{\includegraphics[width=0.4\columnwidth]{./mnist/250_nmse_valid_time}}~
\subfloat[]{\includegraphics[width=0.4\columnwidth]{./mnist/250_f_measure_valid_time}}~
\caption{Predictive performance over clock time on the \textsc{mnist} data with the observation size $K = 250$.}
\label{fig:mnist_time}
\end{figure}
